A Review on Multi-Label Learning Algorithms

### 2018-01-13 Paper/Presentation/mll_review.tex
update report

%------------------------------------------------
\section{Introduction} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
\subsection{Problem Definition}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Single-label supervised learning
\begin{itemize}
	\item Applied to classification
	\item Supervised: Given dataset $\{ (x_i, y_i)\}, i = 1, \dots N, x \in X, y \in Y$
	\item Goal is to learn a model $f: X \rightarrow Y$
\end{itemize}

@@

%------------------------------------------------
\subsection{Algorithm Strategies}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Label search space $\mathbb{S_Y}$ grows exponentially as a function of $|Y|$: 
\begin{itemize}
	\item e.g. for $|Y|=20, |\mathbb{S_Y}| = 2 ^ {|\mathbb{P(Y)}|} = 2^{20} \ge 10^6$
\end{itemize}
Solution: integrate in the learning process potential label correlations.
This work examines algorithms grouped in three broad categories:

@@

Group algorithms in two categories:
\begin{itemize}
	\item \emph{Problem Transformation Methods: }Transform the learning problem into other well-established learning scenarios (fit data to algorithm philosophy)
	\item \emph{Algorithm Adaptation Methods: }Adapt popular learning techniques to deal with multi-label data directly (fit algorithm to data philosophy)
\end{itemize}
\end{frame}

%------------------------------------------------

\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.75]{images/aa.png}
	\end{center}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.7]{images/pt.png}
	\end{center}
\end{figure}
\end{frame}

%------------------------------------------------
\subsection{Problem Transformation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Problem Transformation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Binary Relevance}

\begin{itemize}
	\item Decompose to $q$ independent binary classification problems, $h_i(x)$
	\item Cross-train on $q$ binary training sets (one for each $y_i$)
	\item Predict labels of unseen $x$ by evaluating each classifier $h_i(x)$
	\item Output labels where  $h_i(x) > 0$ else $\underset{1 \geq i \geq q}{argmax} \{h_i(x))\}$ 
\end{itemize}

@@

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
	\item Second-order approach algorithm
	\item Transform the problem into a label ranking problem
	\item Ranking implemented by pairwise comparison techniques
	\item For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison
	\item Construct training set per label pairs considering the example's relevance
	\item For unknown instance, get the overall classifiers' votes
	\item Virtual label $y_v$ as artificial splitting point between relevant and irrelevant labels
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Smooth the class-imbalance
	\item Classifier's number grows from linear to quadratic scale
	\begin{itemize}
		\item Improvement: Exact or approximate pruning to reduce classifier's number to be queried
	\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
	\item High-order approach algorithm
	\item Decompose to an ensemble of multi-class classification problems
	\item Each component targets a random subset of $Y$, inducing a multi-class classifier by Label Powerset (LP) techniques
	\item Convert training set into a multi-class set, treating each label set as a new class
	\item Each example is reassigned with the mapped single-label participating in multi-class classifier induction
	\item For unknown $x$, counts the maximum and actual number of votes
	\item Label set is relevant when the actual number of votes exceeds
half of the maximum ones
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Incompleteness: predicts only label sets included in the training set
	\item Inefficiency: large $Y$ implies high training complexity.Improve by invoking LP only on random k-labelsets and ensemble learning to LP classifiers
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Algorithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
	\item First-order approach algorithm, adapting knn techniques
	\item Lazy learning and Bayesian reasoning
	\item Maximum a posteriori (MAP) rule to make prediction by reasoning and embody label info in the neighbours
	\item For new instances, $N(x)$ represents the set of its knn (uses Euclidean distance)
	\item Posterior probability $\mathbb{P}(H_j|C_j)$ and $\mathbb{P}(\neg H_j|C_j)$, where $C_j$ is the knn of $x$ and $H_j$ is the event that $x$ has the label $y_j$
	\item Predict relevant label set based on which probability is higher(MAP rule)
	\item Frequency counting strategy:
	\begin{enumerate}
		\item Estimation of prior probabilities ($\mathbb{P}(H_j)$ \& $\mathbb{P}(\neg H_j)$) using a smoothing parameter $s$ (usually $s=1$)
		\item Estimation of likelyhoods (($\mathbb{P}(C_j|H_j)$ \& $\mathbb{P}(C_j|\neg H_j)$)
	\end{enumerate}

>>>>

%------------------------------------------------
\section{Introduction} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
\subsection{Problem Definition}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Single-label supervised learning
\begin{itemize}
	\item Applied to classification
	\item Supervised: Dataset $\{ (x_i, y_i)\}, i = 1, \dots N, x \in X, y \in Y$
	\item Goal is to learn a model $f: X \rightarrow Y$
\end{itemize}

@@

%------------------------------------------------
\subsection{Algorithm Strategies}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Label search space $\mathbb{S_Y}$ grows exponentially as a function of $|Y|=q$
\begin{itemize}
	\item e.g. for $q=20, |\mathbb{S_Y}| = 2 ^ {|\mathbb{P(Y)}|} = 2^{20} \ge 10^6$
\end{itemize}
Solution: integrate in the learning process potential label correlations.
This work examines algorithms grouped in three broad categories:

@@

Group algorithms in two categories:
\begin{itemize}
	\item \emph{Problem Transformation Methods: }Transform the learning problem into other well-established learning scenarios (fit data to algorithm philosophy)
	\item \emph{Algorithm Adaptation Methods: }Adapt popular learning techniques to deal with multi-label data directly (fit algorithm to data philosophy)
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Problem Transformation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Problem Transformation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.7]{images/pt.png}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Binary Relevance}

\begin{itemize}
	\item Decompose multi-label problem to $q$ independent binary classification problems
	\item Construct $q$ binary (one-vs-all) training sets (one for each $y_i$)
	\item Cross-train each binary classifier $h_i(x)$ on its respective dataset

	\item Predict labels of an unseen $x$ by evaluating each classifier $h_i(x)$
	\item Output labels where  $h_i(x) > 0$ or $\underset{1 \geq i \geq q}{argmax} \{h_i(x))\}$, if none
\end{itemize}

@@

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
	\item Second-order approach algorithm
	\item Transform the problem into a label ranking problem
	\item Ranking implemented by pairwise comparison techniques
	\item For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison
	\item Construct training set per label pairs considering the example's relevance
	\item For unknown instance, get the overall classifiers' votes
	\item Virtual label $y_v$ as artificial splitting point between relevant and irrelevant labels
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Smooth the class-imbalance
	\item Classifier's number grows from linear to quadratic scale
	\begin{itemize}
		\item Improvement: Exact or approximate pruning to reduce classifier's number to be queried
	\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
	\item High-order approach algorithm
	\item Decompose to an ensemble of multi-class classification problems
	\item Each component targets a random subset of $Y$, inducing a multi-class classifier by Label Powerset (LP) techniques
	\item Convert training set into a multi-class set, treating each label set as a new class
	\item Each example is reassigned with the mapped single-label participating in multi-class classifier induction
	\item For unknown $x$, counts the maximum and actual number of votes
	\item Label set is relevant when the actual number of votes exceeds
half of the maximum ones
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Incompleteness: predicts only label sets included in the training set
	\item Inefficiency: large $Y$ implies high training complexity.Improve by invoking LP only on random k-labelsets and ensemble learning to LP classifiers
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Algorithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.75]{images/aa.png}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
	\item First-order approach algorithm, adapting knn techniques
	\item Lazy learning and Bayesian reasoning
	\item Maximum a posteriori (MAP) rule to make prediction by reasoning and embody label info in the neighbours
	\item For new instances, $N(x)$ represents the set of its knn (uses Euclidean distance)
	\item Posterior probability $\mathbb{P}(H_j|C_j)$ and $\mathbb{P}(\neg H_j|C_j)$, where $C_j$ is the knn of $x$ and $H_j$ is the event that $x$ has the label $y_j$
	\item Predict relevant label set based on which probability is higher(MAP rule)
	\item Frequency counting strategy:
	\begin{enumerate}
		\item Estimation of prior probabilities ($\mathbb{P}(H_j)$ \& $\mathbb{P}(\neg H_j)$) using a smoothing parameter $s$ (usually $s=1$)
		\item Estimation of likelyhoods (($\mathbb{P}(C_j|H_j)$ \& $\mathbb{P}(C_j|\neg H_j)$)
	\end{enumerate}
